Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Style improvements

\subsubsection{Contents}
Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).

@@

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Category & Maintainability Score & Number of Refactorings \\ \midrule
\rowcolor[HTML]{FFCCC9}
Common Hierarchy & 0,63 & 27 \\
Sibling & 0,53 & 664 \\
No Direct Superclass & 0,11 & 295 \\
Same Method & 0,06 & 740 \\
\rowcolor[HTML]{FFCCC9}
Superclass & 0,03 & 68 \\
Same Class & 0,02 & 1273 \\
External Superclass & 0,01 & 209 \\
\rowcolor[HTML]{FFCCC9}
No Indirect Superclass & -0,06 & 36 \\
Same Interface & -0,07 & 269 \\
\rowcolor[HTML]{FFCCC9}
First Cousin & -0,19 & 54 \\
External Ancestor & -0,28 & 154 \\
\rowcolor[HTML]{FFCCC9}
Ancestor & -0,52 & 5 \\ \bottomrule
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

@@

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Return Value & Maintainability Score & Number of Refactorings \\ \midrule
Return & 0,20 & 421 \\
Void & 0,19 & 2052 \\
Declare & 0,03 & 1318 \\
\rowcolor[HTML]{FFCCC9}
Assign & -1,29 & 3 \\ \bottomrule
\end{tabular}
\caption{Maintainability scores for different return values}
\label{tab:return}
\end{table}

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/flow}
  \caption{Influence of number of method parameters on system maintainability.}
  \label{fig:arguments}
\end{figure}

>>>>

\subsubsection{Contents}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).

@@

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Category}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
\rowcolor[HTML]{FFCCC9}
Common Hierarchy & 0,63 & 27 \\
Sibling & 0,53 & 664 \\
No Direct Superclass & 0,11 & 295 \\
Same Method & 0,06 & 740 \\
\rowcolor[HTML]{FFCCC9}
Superclass & 0,03 & 68 \\
Same Class & 0,02 & 1273 \\
External Superclass & 0,01 & 209 \\
\rowcolor[HTML]{FFCCC9}
No Indirect Superclass & -0,06 & 36 \\
Same Interface & -0,07 & 269 \\
\rowcolor[HTML]{FFCCC9}
First Cousin & -0,19 & 54 \\
External Ancestor & -0,28 & 154 \\
\rowcolor[HTML]{FFCCC9}
Ancestor & -0,52 & 5 \\ \bottomrule
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

@@

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
Return & 0,20 & 421 \\
Void & 0,19 & 2052 \\
Declare & 0,03 & 1318 \\
\rowcolor[HTML]{FFCCC9}
Assign & -1,29 & 3 \\ \bottomrule
\end{tabular}
\caption{Maintainability scores for different return values}
\label{tab:return}
\end{table}

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/arguments}
  \caption{Influence of number of method parameters on system maintainability.}
  \label{fig:arguments}
\end{figure}
